Incentivizing Exploration with Heterogeneous Utilities

### 2017-12-04 paper.tex
fixed a citation error

\section{Conclusion}
In this paper, we study the incentivizing exploration problem with heterogeneous user preferences, which generalize the problem setting studied by \citet{frazier2014incentivizing} and \citet{han2015incentivizing}. We propose a simple policy that mostly exploits and occasionally incentivizing exploration, which can achieve $O(N^2+M(\log(T))^2)$ cumulative expected regret with $O(N^2)$ payment budget.

>>>>

\section{Conclusion}
In this paper, we study the incentivizing exploration problem with heterogeneous user preferences, which generalize the problem setting studied by \cite{frazier2014incentivizing} and \cite{han2015incentivizing}. We propose a simple policy that mostly exploits and occasionally incentivizing exploration, which can achieve $O(N^2+M(\log(T))^2)$ cumulative expected regret with $O(N^2)$ payment budget.
